\thetitle

### 2010-01-22 doc/paper.tex
doc: Fix some spelling/grammar bugs Adam noticed.
Ignore-this: 14d924069b65821274815be53efa212b

darcs-hash:20100122125228-bab43-44cba8fb50f03ad6e0c33cbb8ec5cb84b970263f.gz

The prototype implementation described in \cite{alur} was developed in a conventional programming language using libraries that use ordinary floating point arithmetic \todo{which language/libraries exactly?}. The potential for bugs and floating point artifacts inherent in this approach limit the confidence one can justifiably have in safety judgements made by such an implementation. In this report, we describe a reimplementation of the basic technique in Coq, a proof assistant based on a rich type theory that also functions as a programming language, letting one develop ``certified'' programs: programs whose correctness is proved formally within the system. In our case, the program will be one that produces machine-checked proofs of hybrid system safety, obtained using the abstraction method.

@@

We now say that there is a (concrete) \emph{continuous transition} from a state |(l, p)| to a state |(l', p')| if |l = l'| and there is a nonnegative duration |d| such that |p' = flow l p d| with the invariant for |l| holding at every point along the way:

@@

Where continuous transitions describe the flow of continuous variables, \emph{discrete} transitions between locations describe the logic of the software system. Each such transition is comprised of two components: a \emph{guard} predicate, and a \emph{reset} function. The former defines a subset of the continous state space in which the transition is enabled (permitted), while the latter describes an instantaneous change applied as a side effect of the transition, as seen in the following definition of the discrete transition relation:

@@

As mentioned before, the set of reachable states represent the possible behaviors exhibited by a hypothetical real-world implementation of the hybrid system (as software running on a device with sensor and actuators).

@@

% repeat somewhere that an overestimator could just return "true" all teh time, but that would make everything reachable, makign the thing useless for unreachability (and hence, safety) determination.
% and repeat somewhere that overestimation is all about inclusion of predicates, heuristics. basically, this paragraph:

>>>>

The prototype implementation described in \cite{alur} was developed in a conventional programming language using libraries that use ordinary floating point arithmetic \todo{which language/libraries exactly?}. The potential for bugs and floating point artifacts inherent in this approach limits the confidence one can justifiably have in safety judgements made by such an implementation. In this report, we describe a reimplementation of the basic technique in Coq, a proof assistant based on a rich type theory that also functions as a programming language, letting one develop ``certified'' programs: programs whose correctness is proved formally within the system. In our case, the program will be one that produces machine-checked proofs of hybrid system safety, obtained using the abstraction method.

@@

We now say that there is a (concrete) \emph{continuous transition} from a state |(l, p)| to a state |(l', p')| if |l = l'| and there is a non-negative duration |d| such that |p' = flow l p d| with the invariant for |l| holding at every point along the way:

@@

Where continuous transitions describe the flow of continuous variables, \emph{discrete} transitions between locations describe the logic of the software system. Each such transition is comprised of two components: a \emph{guard} predicate, and a \emph{reset} function. The former defines a subset of the continuous state space in which the transition is enabled (permitted), while the latter describes an instantaneous change applied as a side effect of the transition, as seen in the following definition of the discrete transition relation:

@@

As mentioned before, the set of reachable states represents the possible behaviors exhibited by a hypothetical real-world implementation of the hybrid system (as software running on a device with sensor and actuators).

@@

% repeat somewhere that an overestimator could just return "true" all the time, but that would make everything reachable, makign the thing useless for unreachability (and hence, safety) determination.
% and repeat somewhere that overestimation is all about inclusion of predicates, heuristics. basically, this paragraph:
